### 2014-02-12 classicthesis/Chapters/Background.tex
structuurswijziging + parttext
logischere opzet background

Learning-to-Rank algorithms can be classified into three approaches: the pointwise approach, the pairwise approach and the listwise approach, on which we will elaborate in the subsequent chapters.

\chapter{Benchmark Datasets}
\chapter{Pointwise Approach}
\chapter{Pairwise Approach}
\chapter{Listwise Approach}
\chapter{Summary}

>>>>

Learning-to-Rank algorithms can be classified into three approaches: the pointwise approach, the pairwise approach and the listwise approach. In the following chapters we will summarize the different approaches in Learning-to-Rank.

\section{Pointwise Approach}

\section{Pairwise Approach}
\section{Listwise Approach}
